%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Shelby}{Bachman}

\position{Phd Candidate}
\address{Davis School of Gerontology, University of Southern California,
Los Angeles, CA}

\email{\href{mailto:sbachman@usc.edu}{\nolinkurl{sbachman@usc.edu}}}
\homepage{shelbybachman.github.io}
\orcid{0000-0002-4460-4661}
\github{shelbybachman}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {March 2021}
    {Shelby Bachman~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\hypertarget{research-experience}{%
\section{Research Experience}\label{research-experience}}

\hypertarget{awards-funding}{%
\section{Awards \& Funding}\label{awards-funding}}

\hypertarget{publications-peer-reviewed}{%
\section{Publications
(peer-reviewed)}\label{publications-peer-reviewed}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-bachman_locus_2021}{}%
\CSLLeftMargin{1. }
\CSLRightInline{Bachman, S. L., Dahl, M. J., Werkle-Bergner, M., Düzel,
S., Forlim, C. G., Lindenberger, U., Kühn, S., \& Mather, M. (2021).
Locus coeruleus MRI contrast is associated with cortical thickness in
older adults. \emph{Neurobiology of Aging}, \emph{100}, 72--82.
\url{https://doi.org/10.1016/j.neurobiolaging.2020.12.019}}

\leavevmode\hypertarget{ref-kurvers_combining_2018}{}%
\CSLLeftMargin{2. }
\CSLRightInline{Kurvers, R. H. J. M., Zoete, A. de, Bachman, S. L.,
Algra, P. R., \& Ostelo, R. (2018). Combining independent decisions
increases diagnostic accuracy of reading lumbosacral radiographs and
magnetic resonance imaging. \emph{PLOS ONE}, \emph{13}(4), e0194128.
\url{https://doi.org/10.1371/journal.pone.0194128}}

\leavevmode\hypertarget{ref-arbogast_effectiveness_2018}{}%
\CSLLeftMargin{3. }
\CSLRightInline{Arbogast, H., Patao, M., Demeter, N., Bachman, S.,
Devietti, E., Upperman, J. S., \& Burke, R. V. (2018). The effectiveness
of installing a speed hump in reducing motor vehicle accidents involving
pedestrians under the age of 21. \emph{Journal of Transport \& Health},
\emph{8}, 30--34. \url{https://doi.org/10.1016/j.jth.2017.11.004}}

\leavevmode\hypertarget{ref-bachman_observed_2016}{}%
\CSLLeftMargin{4. }
\CSLRightInline{Bachman, S. L., Salzman, G. A., Burke, R. V., Arbogast,
H., Ruiz, P., \& Upperman, J. S. (2016). Observed child restraint misuse
in a large, urban community: Results from three years of inspection
events. \emph{Journal of Safety Research}, \emph{56}, 17--22.
\url{https://doi.org/10.1016/j.jsr.2015.11.005}}

\leavevmode\hypertarget{ref-bachman_schoolhospital_2015}{}%
\CSLLeftMargin{5. }
\CSLRightInline{Bachman, S. L., Arbogast, H., Ruiz, P., Farag, M.,
Demeter, N. E., Upperman, J. S., \& Burke, R. V. (2015). A
School--Hospital Partnership Increases Knowledge of Pedestrian and Motor
Vehicle Safety. \emph{Journal of Community Health}, \emph{40}(6),
1057--1064. \url{https://doi.org/10.1007/s10900-015-0031-3}}

\leavevmode\hypertarget{ref-lin_assessment_2015}{}%
\CSLLeftMargin{6. }
\CSLRightInline{Lin, A. C., Salzman, G. A., Bachman, S. L., Burke, R.
V., Zaslow, T., Piasek, C. Z., Edison, B. R., Hamilton, A., \& Upperman,
J. S. (2015). Assessment of Parental Knowledge and Attitudes Toward
Pediatric Sports-Related Concussions. \emph{Sports Health: A
Multidisciplinary Approach}, \emph{7}(2), 124--129.
\url{https://doi.org/10.1177/1941738115571570}}

\leavevmode\hypertarget{ref-clewett_age-related_2014}{}%
\CSLLeftMargin{7. }
\CSLRightInline{Clewett, D., Bachman, S., \& Mather, M. (2014).
Age-related reduced prefrontal-amygdala structural connectivity is
associated with lower trait anxiety. \emph{Neuropsychology},
\emph{28}(4), 631--642. \url{https://doi.org/10.1037/neu0000060}}

\leavevmode\hypertarget{ref-bachman_impact_2014}{}%
\CSLLeftMargin{8. }
\CSLRightInline{Bachman, S. L., Demeter, N. E., Lee, G. G., Burke, R.
V., Valente, T. W., \& Upperman, J. S. (2014). The Impact of Trauma
Systems on Disaster Preparedness: A Systematic Review. \emph{Clinical
Pediatric Emergency Medicine}, \emph{15}(4), 296--308.
\url{https://doi.org/10.1016/j.cpem.2014.09.004}}

\leavevmode\hypertarget{ref-burke_using_2014}{}%
\CSLLeftMargin{9. }
\CSLRightInline{Burke, R. V., Kim, T. Y., Bachman, S. L., Iverson, E.
I., \& Berg, B. M. (2014). Using Mixed Methods to Assess Pediatric
Disaster Preparedness in the Hospital Setting. \emph{Prehospital and
Disaster Medicine}, \emph{29}(6), 569--575.
\url{https://doi.org/10.1017/S1049023X14001137}}

\hypertarget{preprints-not-peer-reviewed}{%
\section{Preprints (not
peer-reviewed)}\label{preprints-not-peer-reviewed}}

\hypertarget{bibliography}{}
\leavevmode\hypertarget{ref-clewett_survival_2020}{}%
\CSLLeftMargin{1. }
\CSLRightInline{Clewett, D., Dunsmoor, J., Bachman, S., Phelps, E., \&
Davachi, L. (2020). \emph{Survival of the salient: Emotion rescues
otherwise forgettable memories via neural reactivation and post-encoding
hippocampal connectivity} {[}Preprint{]}. Neuroscience.
\url{https://doi.org/10.1101/2020.07.07.192252}}

\hypertarget{conference-presentations-talks}{%
\section{Conference Presentations \&
Talks}\label{conference-presentations-talks}}

\hypertarget{poster-presentations}{%
\section{Poster Presentations}\label{poster-presentations}}

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

\hypertarget{mentoring}{%
\section{Mentoring}\label{mentoring}}

\hypertarget{university-service}{%
\section{University Service}\label{university-service}}

\hypertarget{academic-service}{%
\section{Academic Service}\label{academic-service}}

\hypertarget{statistical-training}{%
\section{Statistical Training}\label{statistical-training}}

\hypertarget{skills}{%
\section{Skills}\label{skills}}

\end{document}
